A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-09-20 sections/appendix/descrete_event_simulation/main.tex
Fix failing doctests
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

This model will be studied by using  
\lstinline[style=pystyle]{ambulance_game}.
Install the created library in your python environment, by running the 
following command in the command line:
\begin{lstlisting}[style=terminalstyle]
    $ pip install ambulance_game
\end{lstlisting}

@@

The above block code outputs the fourth individual record from the simulation
object.
The simulation object can be used to view the every event that occurred in the 
simulation 
The data records can then be used to get overall performance measures about the
constructed queueing model.
The overall waiting time that individuals wait in waiting zone 1 can be acquired 
by running:

@@

\begin{lstlisting}[style=terminalstyle]
    $ pip install ambulance_game
\end{lstlisting}

@@

To get the simulation object with all the data records, the following code can be
used:
\begin{lstlisting}[style=pystyle]
    >>> import ambulance_game as abg
    >>> Simulation = abg.simulation.simulate_model(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     seed_num=0,
    ... )
    >>> Simulation.get_all_records()[4]
    Record(id_number=2, customer_class=0, node=2, arrival_date=0.5727571550618586, waiting_time=0.0, service_start_date=0.5727571550618586, service_time=0.7159547497671506, service_end_date=1.2887119048290092, time_blocked=0.0, exit_date=1.2887119048290092, destination=-1, queue_size_at_arrival=1, queue_size_at_departure=3)

@@

From a single run of the simulation the data records can be used the get the
average for certain performance measures. 
The following code can be used to get the mean waiting time, blocking time, 
service time and the proportion of individuals within target.

@@

To eliminate any stochasticity in the simulation, the simulation can be run
numerous times and get the average performance measures out of all the runs.

@@

    >>> np.nansum(probs)
    1.0

>>>>

This model will be studied by using  
\lstinline[style=pystyle]{ambulance_game}.
Install the created library in your python environment, by running the 
following command in the command line:
\begin{lstlisting}[style=terminalstyle]
    $ python -m pip install ambulance_game
\end{lstlisting}

@@

The above block code outputs the fourth individual record from the simulation
object.
The simulation object can be used to view every event that occurred in the 
simulation 
The data records can then be used to get overall performance measures about the
constructed queueing model.
The overall waiting time that individuals wait in waiting zone 1 can be acquired 
by running:

@@

\begin{lstlisting}[style=terminalstyle]
    $ python -m pip install ambulance_game
\end{lstlisting}

@@

To get the simulation object with all the data records, the following code can be
used:

\begin{lstlisting}[style=pystyle]
    >>> import ambulance_game as abg
    >>> Simulation = abg.simulation.simulate_model(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     seed_num=0,
    ... )
    >>> Simulation.get_all_records()[4]
    Record(id_number=2, customer_class=0, node=2, arrival_date=0.5727571550618586, waiting_time=0.0, service_start_date=0.5727571550618586, service_time=0.7159547497671506, service_end_date=1.2887119048290092, time_blocked=0.0, exit_date=1.2887119048290092, destination=-1, queue_size_at_arrival=1, queue_size_at_departure=3)

@@

From a single run of the simulation the data records can be used to get the
average for certain performance measures. 
The following code can be used to get the mean waiting time, blocking time, 
service time and the proportion of individuals within target.

@@

To reduce the effects of stochasticity in the simulation, the simulation can be run
numerous times and get the average performance measures out of all the runs.

@@

    >>> total = np.nansum(probs)
    >>> np.round(total, decimals=5)
    1.0
